---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countries

<!-- badges: start -->
[![Project Status: WIP](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

A tool for generating lists of country names based on various definitions and organising them into different administrative, socio-economic, and/or political groupings.

## Installation

`countries` is still in active development and is not yet available on [CRAN](https://cran.r-project.org/).

You can install the development version of `countries` from [GitHub](https://github.com/katilingban/countries) with:

```{r install_github, echo = TRUE, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("katilingban/countries")
```

## What does `countries` do?

## Citation

If you find the `countries` package useful, please cite using the suggested citation provided by a call to the `citation` function as follows:

```{r citation, echo = TRUE, eval = FALSE}
citation("countries")
```

## Community guidelines

Feedback, bug reports, and feature requests are welcome; file issues or seek support [here](https://github.com/katilingban/countries/issues). If you would like to contribute to the package, please see our [contributing guidelines](https://katilingban.io/countries/CONTRIBUTING.html).

This project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

